Synthesis of Linear Functional Programs

### 2021-04-30 article/article.tex
more notes
write one more line :)

This work explores the process of synthetising linear functional programs from types based in linear logic, leveraging the Curry-Howard correspondence.
- forma resumida a correspondência: "obs que proposições lógicas correspondem a tipos e programas bem tipificados correspondem a provas das proposições"
Having a type be a proposition in linear logic, and from the Curry-Howard correspondence, we can relate a proof of that proposition directly to a linear functional program - finding a proof is finding a program with that type, so we formulate the synthesis as proof search in this logic.

>>>>

This work explores the process of synthetising linear functional programs from types based in linear logic, leveraging the Curry-Howard correspondence.
Said correspondence states that propositions in a logic have a direct mapping to types, and well typed programs also have a one to one correspendence to proofs of those propositions.
As such, having a type be a proposition in linear logic, we can relate a proof of that proposition directly to a linear functional program - finding a proof is finding a program with that type, and so we formulate the synthesis as proof search in linear logic.
